Market Simulator

### 2020-08-17 analysis/05_market_simulator.Rmd
Persona input

####################################################################

beta_persona <- as.data.frame(matrix(rep(0), nrow = 38))

beta_persona$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")

# Persona Reactive Element

@@

  #Persona 1
    beta_persona$p1_value <- 0
    beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1
  #Persona 2
    beta_persona$p2_value <- 0
    beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_trust_in_charity] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_amount] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_12] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_personal_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_family_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religious_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_sport_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_art_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_labor_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_environmental_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_professional_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_humanitarian_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_consumer_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_other_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_marital_status] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_education] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_income] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_race] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_age] <- 1
  #Persona 3
    beta_persona$p3_value <- 0
    beta_persona$p3_value[beta_persona$levels == 'Persona 3'] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
    beta_persona

@@

beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))

beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")

# Persona Reactive Element

beta_persona_test$p1 <- 1

beta_persona_test$p2 <- 2

beta_persona_test$p3 <- 3

persona1 <- persona_data[,2]

p_beta1 <- as.matrix(public_political_social_charity_demo) %*%

  as.matrix(persona1) %*% beta_persona_test[,3]

>>>>

# persona beta levels -----

beta_persona <- as.data.frame(matrix(rep(0), nrow = 61))

beta_persona$levels = c("Intercept",
                        "Follow National News", 
                        "Follow International News",
                        "News Medium - TV",
                        "News Medium - Print",
                        "News Medium - Online",
                        "News Medium - Social Media",
                        "News Medium - Radio",
                        "News Medium - Email",
                        "News Medium - Newsapp",
                        "Follow Government or Public Affairs", 
                        "No Travel to Developing Countries", 
                        "Political Preference", 
                        "Trust in Political Institutions",
                        "Others Should be Charitable",
                        "Worship Service Attendence",
                        "Religious Importance",
                        "Religion - Protestant",
                        "Religion - Christian Orthodox",
                        "Religion - Jewish",
                        "Religion - Muslim",
                        "Religion - Sikh",
                        "Religion - Hindu",
                        "Religion - Buddhist",
                        "Religion - Atheist",
                        "Religion - Other",
                        "Chartiy Trust Importance",
                        "Trust in Charity", 
                        "Donation Frequency", 
                        "Donation Amount",
                        "Volunteer 12 Months",
                        "Volunteer Frequence",
                        "Personal Activism",
                        "Family Activism",
                        "Religious Membership", 
                        "Sport or Recreational Membership", 
                        "Art, Music, or Educational Membership",
                        "Labor Union Membership",
                        "Political Party Membership",
                        "Environmental Organization Membership",
                        "Professional Association", 
                        "Humanitarian or Charity Membership",
                        "Consumer Organization Membership",
                        "Other Organization Membership",
                        "Gender - Female",
                        "Gender - Transgender",
                        "Gender - Prefer not to say",
                        "Gender - Other",
                        "Marital Status - Widowed",
                        "Marital Status - Divorced",
                        "Marital Status - Separated",
                        "Marital Status - Never Married",
                        "Education", 
                        "Income", 
                        "Race - White", 
                        "Race - Black", 
                        "Race - American Indian", 
                        "Race - Asian", 
                        "Race - Pacific Islander", 
                        "Race - Other", 
                        "Age")

# Persona Reactive Element --------

@@

  #Persona 1
    beta_persona$p1_value <- 0

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1

  #Persona 2
    beta_persona$p2_value <- 0

    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_trust_in_charity] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_amount] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_12] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_personal_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_family_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religious_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_sport_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_art_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_labor_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_environmental_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_professional_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_humanitarian_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_consumer_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_other_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_marital_status] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_education] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_income] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_race] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_age] <- 1

  #Persona 3
    beta_persona$p3_value <- 0

    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
    beta_persona

@@

# beta_persona_test <- as.data.frame(matrix(rep(0), nrow = 38))
# 
# beta_persona_test$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")
# 
# 
# 
# # Persona Reactive Element
# 
# beta_persona_test$p1 <- 1
# 
# beta_persona_test$p2 <- 2
# 
# beta_persona_test$p3 <- 3
#         
# persona1 <- persona_data[,2]
# 
# p_beta1 <- as.matrix(public_political_social_charity_demo) %*%   
#   
#   as.matrix(persona1) %*% beta_persona_test[,3]
